Extending the WebID Protocol with Access Delegation

### 2012-08-25 paper.tex
use autoref instead of ref

\usepackage[
pdftex,
bookmarks=true,
%hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}

@@

\paragraph{Keeping views distinct}-
First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resource $R$ seen when connected as the different user $U_2$. 
This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones. 
This can be illustrated using N3 graphs, by specifying a relation between a view on a resource (using a yet to be settled on vocabulary), and a graph which is the log:semantics of that view (cf. Listing~\ref{listing:views}). 
It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$. 
This requires carefully keeping identified information that was aimed at different users separate, perhaps by creating different graph stores: one for public - non authenticated - information, and one graph store for each user the server needs to authenticate as.

@@

The Capulet FreedomBox Guard having verified that this request does indeed come from the origin server of Romeo's profile
\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.  
In Section~\ref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.

@@

The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in Listing \ref{listing:webid1}.

@@

%\paragraph{Data import}
A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely \textit{import of external data}.
%Figure \ref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
Since WebID profiles can contain personal information that is in need of protection, access to such data should be restricted with the WebID protocol.
Although a user may (or may not in the case of a periodically executed automatic synchronization process) initiate the import procedure manually via the OntoWiki user interface, the actual fetching is done in the background.
An OntoWiki instance does not know of any private keys of users of the system.
Thus the system is not able to use that information when requesting data.
With WebID access delegation though, the profile can be fetched on behalf of the user instead.

@@

The use cases for CORS are slightly different from the ones for our delegation proposal. 
In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), as it needs to alert the remote service that the request originates from a particular agent.
The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the JavaScript trust relation.
In the Section~\ref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the \textit{principal} and the \textit{secretary}. The vagueness of the \lstinline|Origin| identity of the \textit{principal} in CORS makes a lot of this more difficult.

>>>>

\usepackage[
pdftex,
bookmarks=true,
%hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}
\def\sectionautorefname{Section}% redefine the label for section links

@@

\paragraph{Keeping views distinct}-
First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resource $R$ seen when connected as the different user $U_2$. 
This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones. 
This can be illustrated using N3 graphs, by specifying a relation between a view on a resource (using a yet to be settled on vocabulary), and a graph which is the log:semantics of that view (cf. \autoref{listing:views}). 
It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$. 
This requires carefully keeping identified information that was aimed at different users separate, perhaps by creating different graph stores: one for public - non authenticated - information, and one graph store for each user the server needs to authenticate as.

@@

The Capulet FreedomBox Guard having verified that this request does indeed come from the origin server of Romeo's profile
\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.  
In \autoref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.

@@

The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in \autoref{listing:webid1}.

@@

%\paragraph{Data import}
A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely \textit{import of external data}.
%\autoref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
Since WebID profiles can contain personal information that is in need of protection, access to such data should be restricted with the WebID protocol.
Although a user may (or may not in the case of a periodically executed automatic synchronization process) initiate the import procedure manually via the OntoWiki user interface, the actual fetching is done in the background.
An OntoWiki instance does not know of any private keys of users of the system.
Thus the system is not able to use that information when requesting data.
With WebID access delegation though, the profile can be fetched on behalf of the user instead.

@@

The use cases for CORS are slightly different from the ones for our delegation proposal. 
In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), as it needs to alert the remote service that the request originates from a particular agent.
The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the JavaScript trust relation.
In the \autoref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the \textit{principal} and the \textit{secretary}. The vagueness of the \lstinline|Origin| identity of the \textit{principal} in CORS makes a lot of this more difficult.
